A Multi-telescope Campaign on \frb: Implications for the FRB Population

### 2017-04-26 repeater-vladata.tex
modified obs table

@@

% ** be sure future high-burst rate paper from Arecibo doesn't rule this out **

@@

Many new models for the origin of FRBs have been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}. The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which is not a prediction of models that scale with stellar mass or star formation \citep{2017arXiv170400022N}. These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of the magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.

%Also, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.

This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories. If we assume that \frb\ is representative of all FRBs, we can use it to constrain the physical processes at play in the overall FRB population. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.
%More data is needed to determine if bursts trace intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} or if extrinsic effects also play a role \citep{2015MNRAS.451.3278M, CORDES}.

@@

\includegraphics[width=2\columnwidth]{timeline}
\caption{The top and bottom panels summarize the observations and detections of \frb\ in the 2015 and 2016 campaigns. Circles highlight observations that detected bursts from \frb\ with multiple burst detections indicated with a heavy line. The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes and the solid line shows the simultaneous burst detection. Circled observations with no line indicate observations on the same day that did not overlap. Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 15~GHz, respectively.
\label{fig:sched}}
\end{center}
\end{figure*}

The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA. We coordinated observing between the VLA, Arecibo, Effelsberg, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}. Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.

@@

% ** add mjd colum **

\startlongtable
\begin{deluxetable}{lcccc}
\small
\tablecaption{Table of VLA Observations \label{tab:obs}}
%\centering
%\begin{tabular}{lcccccc}
\startdata
Day & Start time & Duration & Freq. & Bursts \\% & Other Coverage & Other Detections \\
(yyyy-mm-dd) & (hh:mm:ss) & (min) & (GHz) & \\ \hline
2015-11-25 & 3:25:29 & 60 & 1.4 & 0 \\
2015-12-01 & 5:31:31 & 60 & 1.4 & 0 \\
2015-12-03 & 2:53:57 & 60 & 1.4 & 0 \\
2015-12-05 & 4:45:44 & 60 & 1.4 & 0 \\
2015-12-07 & 4:37:50 & 60 & 1.4 & 0 \\
2015-12-09 & 9:29:25 & 60 & 1.4 & 0 \\
2015-12-11 & 9:22:27 & 60 & 1.4 & 0 \\
2015-12-13 & 9:13:7 & 60 & 1.4 & 0 \\
2015-12-15 & 9:6:16 & 60 & 1.4 & 0 \\
2015-12-17 & 8:57:51 & 60 & 1.4 & 0 \\
2016-04-25 & 15:39:33 & 42 & 3 & 0  \\
2016-04-26 & 21:49:35 & 15 & 3 & 0  \\
2016-04-30 & 19:14:46 & 60 & 3 & 0  \\
2016-05-01 & 18:8:21 & 60 & 3 & 0  \\
2016-05-03 & 22:53:26 & 60 & 3 & 0  \\
2016-05-04 & 22:50:30 & 60 & 3 & 0  \\
2016-05-06 & 18:25:12 & 60 & 3 & 0  \\
2016-05-07 & 19:34:13 & 60 & 3 & 0  \\
2016-05-08 & 19:30:20 & 60 & 3 & 0  \\
2016-05-13 & 17:12:48 & 135 & 3 & 0  \\
2016-05-14 & 17:14:11 & 135 & 3 & 0  \\
2016-05-15 & 17:15:26 & 135 & 3 & 0  \\
2016-05-16 & 16:59:52 & 135 & 3 & 0  \\
2016-05-20 & 16:45:46 & 135 & 3 & 0  \\
2016-05-21 & 16:44:6 & 135 & 3 & 0  \\
2016-05-22 & 16:43:53 & 135 & 3 & 0  \\
2016-05-23 & 16:44:11 & 135 & 3 & 0  \\
2016-05-27 & 16:29:34 & 135 & 3 & 0  \\
2016-08-23 & 17:26:28 & 54 & 3 & 1  \\
2016-09-02 & 15:52:17 & 54 & 3 & 2  \\
2016-09-07 & 10:14:50 & 120 & 3 & 1  \\
2016-09-08 & 10:14:40 & 120 & 3 & 0  \\
2016-09-10 & 9:59:36 & 120 & 3 & 0  \\
2016-09-11 & 9:59:49 & 120 & 3 & 0  \\
2016-09-12 & 9:15:19 & 120 & 3 & 1\tablenotemark{a} \\ 
2016-09-13 & 9:23:59 & 120 & 3 & 0  \\
2016-09-14 & 9:20:23 & 120 & 3 & 1\tablenotemark{a,b} \\
2016-09-15 & 9:16:29 & 120 & 3 & 1  \\
2016-09-16 & 9:11:23 & 120 & 3 & 0  \\
2016-09-17 & 8:59:20 & 120 & 3 & 1\tablenotemark{a,b,*,c} \\ 
2016-09-18 & 8:59:27 & 120 & 3 & 1\tablenotemark{a,b,c} \\
2016-09-19 & 8:44:32 & 120 & 3 & 0  \\
2016-09-20 & 8:44:33 & 120 & 3 & 0  \\
2016-09-20 & 17:19:3 & 120 & 6 & 0  \\
2016-09-21 & 9:13:57 & 120 & 6 & 0  \\
2016-09-22 & 9:12:24 & 120 & 6 & 0  \\
\enddata
\tablecomments{Times are in UT. Frequency is the approximate center of the bandwidth.}
\tablenotetext{a}{AMI-LA coverage at 15~GHz.}
\tablenotetext{b}{Arecibo coverage at 1.4~GHz.}
\tablenotetext{*}{Arecibo detection at 1.4~GHz.}
\tablenotetext{c}{Effelsberg coverage at 4.5~GHz.}
%\end{tabular}
%\tablenotetext{a}{}
%\label{tab:obs}
\end{deluxetable}

@@

% ** uncertainties in dm delay? **

Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets. We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively. We used PRESTO \citep{2001PhDT.......123R} to calculate a relative barycentric time correction of 3.8~ms between the VLA and Arecibo at the time of observation.

@@

% ** errorbars on flux densities?

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three bursts with multi-telescope observing coverage. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of 111 mJy and 14 mJy at 3 and 1.4~GHz, respectively. Here we assume a typical pulse width of 2~ms to measure VLA and Arecibo integrated flux densities of 278 and 64 mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the bursts with simultaneous observing coverage are not well described by a power-law model. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.8$ and $\alpha_{3/4.5}<-2.7$. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
% could note that these limits are understated by VLA integrated flux underestimate

\begin{figure}[htb]
\begin{center}
 \includegraphics[width=\columnwidth]{multispec.png}
 \caption{Broadband spectral measurements and limits for three bursts of \frb\ with simultaneous multi-telescope observing coverage (Arecibo at 1.4~GHz, VLA at 3~GHz, and Effelsberg at 4.5~GHz). Measurements are shown with dots and upper limits with triangles. Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold. Overlapping points are offset by tens of MHz in frequency for visualization.
 \label{fig:multi}}
\end{center}
\end{figure}

@@

\begin{table*}
\caption{Properties of \frb\ Bursts at 3~GHz}
\centering
\begin{tabular}{cc|rrr|ccrrrr}
\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observed properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& W 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
(2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 7  			\\
7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 10 			\\	
17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
\end{tabular}
\tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, or AMI-LA.}
\tablenotetext{b}{Detected simultaneously with Arecibo.}
\tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\label{tab:spec}
\end{table*}

@@

The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta \rm{DM}=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. 
%In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$. However, the uncertainty in the peak DM measurement is defined by the signal-to-noise of the burst and how this changes with DM.
The MCMC modeling is more sophisticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.

Figure \ref{fig:dmmodel} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel). The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign. However, we note that the 95\% confidence intervals in DM for multiple bursts are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM. The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
%As noted before, this is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.

>>>>

\author{K.~Stovall}
\affiliation{National Radio Astronomy Observatory, Socorro, NM 87801, USA}

@@

@@

Many new models for the origin of FRBs have been developed in response to the localization of \frb\ \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D, 2017arXiv170208644B, 2017arXiv170300393T}. The association of \frb\ with a compact, persistent radio source is consistent with bursts coming from a young magnetar that powers a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb\ is found in a low-metallicity dwarf galaxy \citep{OPT, 2017arXiv170102370M}, which was not predicted by origin models that scale with stellar mass or star formation \citep{2017arXiv170400022N}. These galaxies are the preferred environment for long GRBs and Type-I superluminous supernovae (LGRB and SLSN-I, respectively), which have been suggested are signatures of the magnetar birth \citep{2008AJ....135.1136M, 2014ApJ...787..138L}.

This paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Arecibo, Effelsberg, the Long-Wavelength Array (LWA), and the Arcminute Microkelvin Imager Large Array (AMI-LA). This includes the first simultaneous detection of an FRB at two observatories, between the VLA and Arecibo. If we assume that \frb\ is representative of all FRBs, we can use it to constrain the physical processes at play in the overall FRB population. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

@@

\includegraphics[width=2\columnwidth]{timeline}
\caption{The top and bottom panels summarize the observations and detections of \frb\ in the 2015 and 2016 campaigns. Circles highlight observations that detected bursts from \frb\ with multiple burst detections indicated with a heavy line. The black dashed lines show the VLA burst detections with simultaneous coverage at other telescopes and the solid line shows the simultaneous burst detection. Circled observations with no line indicate observations on the same day that did not overlap. Symbols show days with observations with letters L, S, C, U referring to radio frequencies of 1.4, 3, 4.5, and 15~GHz, respectively.
% ** add LWA as "V" for VHF?
\label{fig:sched}}
\end{center}
\end{figure*}

The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA. We coordinated observing between the VLA, Arecibo, Effelsberg, LWA, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}. Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.

@@

\startlongtable
\begin{deluxetable}{lcccc}
\small
\tablecaption{Table of VLA Observations \label{tab:obs}}
%\centering
%\begin{tabular}{lcccccc}
\startdata
MJD & Date/time & Duration & Freq. & Bursts \\
 & (ymd/hms) & (min) & (GHz) & \\ \hline
57351 & 2015-11-25/3:25:29 & 60 & 1.4 & 0 \\
57357 & 2015-12-01/5:31:31 & 60 & 1.4 & 0 \\
57359 & 2015-12-03/2:53:57 & 60 & 1.4 & 0 \\
57361 & 2015-12-05/4:45:44 & 60 & 1.4 & 0 \\
57363 & 2015-12-07/4:37:50 & 60 & 1.4 & 0 \\
57365 & 2015-12-09/9:29:25 & 60 & 1.4 & 0 \\
57367 & 2015-12-11/9:22:27 & 60 & 1.4 & 0 \\
57369 & 2015-12-13/9:13:7 & 60 & 1.4 & 0 \\
57371 & 2015-12-15/9:6:16 & 60 & 1.4 & 0 \\
57373 & 2015-12-17/8:57:51 & 60 & 1.4 & 0 \\
57503 & 2016-04-25/15:39:33 & 42 & 3 & 0  \\
57504 & 2016-04-26/21:49:35 & 15 & 3 & 0  \\
% ** symbols in the plot here. missing something from archive?
57508 & 2016-04-30/19:14:46 & 60 & 3 & 0  \\
57509 & 2016-05-01/18:8:21 & 60 & 3 & 0  \\
57511 & 2016-05-03/22:53:26 & 60 & 3 & 0  \\
57512 & 2016-05-04/22:50:30 & 60 & 3 & 0  \\
57514 & 2016-05-06/18:25:12 & 60 & 3 & 0  \\
57515 & 2016-05-07/19:34:13 & 60 & 3 & 0  \\
57516 & 2016-05-08/19:30:20 & 60 & 3 & 0  \\
57521 & 2016-05-13/17:12:48 & 135 & 3 & 0  \\
57522 & 2016-05-14/17:14:11 & 135 & 3 & 0  \\
57523 & 2016-05-15/17:15:26 & 135 & 3 & 0  \\
57524 & 2016-05-16/16:59:52 & 135 & 3 & 0  \\
57528 & 2016-05-20/16:45:46 & 135 & 3 & 0  \\
57529 & 2016-05-21/16:44:6 & 135 & 3 & 0  \\
57530 & 2016-05-22/16:43:53 & 135 & 3 & 0  \\
57531 & 2016-05-23/16:44:11 & 135 & 3 & 0  \\
57535 & 2016-05-27/16:29:34 & 135 & 3 & 0  \\
57523 & 2016-08-23/17:26:28 & 54 & 3 & 1  \\
57533 & 2016-09-02/15:52:17 & 54 & 3 & 2  \\
57538 & 2016-09-07/10:14:50 & 120 & 3 & 1  \\
57539 & 2016-09-08/10:14:40 & 120 & 3 & 0  \\
57541 & 2016-09-10/9:59:36 & 120 & 3 & 0  \\
57542 & 2016-09-11/9:59:49 & 120 & 3 & 0  \\
57543 & 2016-09-12/9:15:19 & 120 & 3 & 1\tablenotemark{d} \\ 
57544 & 2016-09-13/9:23:59 & 120 & 3 & 0  \\
57545 & 2016-09-14/9:20:23 & 120 & 3 & 1\tablenotemark{a,d} \\
57546 & 2016-09-15/9:16:29 & 120 & 3 & 1  \\
57547 & 2016-09-16/9:11:23 & 120 & 3 & 0  \\
57548 & 2016-09-17/8:59:20 & 120 & 3 & 1\tablenotemark{a,*,b,d} \\ 
57549 & 2016-09-18/8:59:27 & 120 & 3 & 1\tablenotemark{a,b,d} \\
57550 & 2016-09-19/8:44:32 & 120 & 3 & 0  \\
57551 & 2016-09-20/8:44:33 & 120 & 3 & 0  \\
57551 & 2016-09-20/17:19:3 & 120 & 6 & 0  \\
57552 & 2016-09-21/9:13:57 & 120 & 6 & 0  \\
57553 & 2016-09-22/9:12:24 & 120 & 6 & 0  \\ \hline
\enddata
\tablecomments{Times are in UT. Frequency is the approximate center of the bandwidth.}
\tablenotetext{a}{Arecibo coverage at 1.4~GHz.}
\tablenotetext{*}{Arecibo detection at 1.4~GHz.}
\tablenotetext{b}{Effelsberg coverage at 4.5~GHz.}
\tablenotetext{c}{LWA coverage at **xx** MHz.}
\tablenotetext{d}{AMI-LA coverage at 15~GHz.}
%\end{tabular}
%\tablenotetext{a}{}
%\label{tab:obs}
\end{deluxetable}

@@

Figure \ref{fig:sgram} shows a dynamic spectrum for this burst with both VLA and Arecibo data. The temporal resolution of the VLA data (5~ms) is much coarser than that of Arecibo, so data were resampled to the Arecibo temporal grid after correcting for barycentric and dispersion measure offsets. We assumed a DM of 560.5 pc cm$^{-3}$ (Hessels et al., in prep) to calculate a dispersion delay of 189 and 734~ms from infinite frequency to the top of the VLA and Arecibo bands, respectively. An error in the DM of 1 pc cm$^{-3}$\ corresponds to a delay time correction error of 0.3 and 1.4~ms for the VLA and Arecibo bands, respectively. We used PRESTO \citep{2001PhDT.......123R} to calculate a relative barycentric time correction of 3.8~ms between the VLA and Arecibo at the time of observation.

@@

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for three bursts with multi-telescope observing coverage. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively. The VLA observations underresolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms. Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $64\pm2$\ mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=1.9$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.5~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the bursts with simultaneous observing coverage are not well described by a power-law model. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo and Effelsberg upper limits at 1.4 and 4.5~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.8$ and $\alpha_{3/4.5}<-2.7$. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.5}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.

\begin{figure}[htb]
\begin{center}
 \includegraphics[width=\columnwidth]{multispec.png}
 \caption{Broadband spectral measurements and limits for three bursts of \frb\ with simultaneous multi-telescope observing coverage (Arecibo at 1.4~GHz, VLA at 3~GHz, and Effelsberg at 4.5~GHz). Measurements are shown with dots and upper limits with triangles. Upper limits assume a pulse width of 2~ms and a $5\sigma$ detection threshold. Errors in flux density are comparable to the symbol size and are not shown. Overlapping points are offset by tens of MHz in frequency for clarity.
 % ** useful to add LWA?
 \label{fig:multi}}
\end{center}
\end{figure}

@@

\begin{table*}
\caption{Properties of \frb\ Bursts Seen by VLA at 3~GHz}
\centering
\begin{tabular}{cc|rrr|ccrrrr}
\multicolumn{2}{c|}{Time} & \multicolumn{3}{c|}{Observed properties} & \multicolumn{6}{c}{Modeled properties} \\ \hline
Calendar day & Burst time   & S/N & $S_{\rm{I, 5~ms}}$	& $S_{\rm{V}}$ 	& DM 			& W 			& $S_{\rm{I,peak}}$ & Center & FWHM & $E_{\rm{int}}$ \\
(2016)       &  (MJD)     &   (image)    & (mJy) 			& (mJy) 		    & (pc cm$^{-3})$ 	& (ms) 			& (mJy) 			& (GHz)  & (MHz) & ($10^{38}$\ erg)\\ \hline
23 Aug & 57623.74402686      & 38 		& 194			& +3				& 567$\pm2$ 		& 2.0$\pm0.2$	 		& 690 		& 2.8 		& 290 & 11 			\\
2 Sep & 57633.67986367      & 179 		& 1500			& --35 				& 568.2$\pm0.2$ 	& 2.05$\pm0.02$			& 3340 		& 3.2 		& 510 & 98				\\
2 Sep\tablenotemark{c} & 57633.69515938 & 15 & 69		& +2				& 562$^{+4}_{-6}$ 	& 2.5$^{+0.9}_{-0.6}$	& $>$430 	& $<$2.5	& $<$290 & 7  			\\
7 Sep & 57638.49937435      & 12 		& 55			& +5 				& 567$^{+7}_{-9}$ 	& 1.3$^{+1.4}_{-0.8}$	& 130 		& 3.1 		& 420 & 3  			\\
12 Sep\tablenotemark{a} & 57643.45730263  & 100 		& 508 & --5 		& 565.6$^{+0.6}_{-0.5}$ & 1.9$\pm0.1$		& 1170 		& 2.8 		& 510 & 34 			\\
14 Sep\tablenotemark{a} & 57645.42958602   & 13 		& 64 & +3			& 563$^{+5}_{-4}$ 	& 1.1$\pm0.7$		 	& 170 		& 2.8 		& 380 & 4  			\\
15 Sep\tablenotemark{c} & 57646.46600650 & 20 & 87		& +1				& 569$\pm5$ 		& 2.5$^{+0.9}_{-1.4}$	& $>$420 	& $<$2.5 	& $<$430 & 10 			\\	
17 Sep\tablenotemark{a,b} & 57648.43691490 & 25 & 111	& +9				& 564$\pm2$ 		& 1.4$^{+0.3}_{-0.4}$	& 260 		& 2.8 		& 470 & 7  			\\
18 Sep\tablenotemark{a} & 57649.45175697   & 36 		& 167 & +1			& 567$\pm2$ 		& 2.1$\pm0.5$		 	& 290 		& 3.0 		& 690 & 12 			\\ \hline
\end{tabular}
\tablecomments{$S_{\rm{V}}$ is the measured circular polarization of the burst, which dominated by systematic effects. All error ranges represent 68\% confidence intervals.}
\tablenotetext{a}{Simultaneously observed by either Arecibo, Effelsberg, or AMI-LA.}
\tablenotetext{b}{Detected simultaneously with Arecibo.}
\tablenotetext{c}{Best-fit Gaussian is not centered in 3~GHz band, so spectral parameters are limits.}
\label{tab:spec}
\end{table*}

@@

The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta \rm{DM}=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. The MCMC modeling is more sophisticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.

Figure \ref{fig:dmmodel} compares the 68\% confidence intervals on the DM for all nine VLA bursts against detection time (top panel) and the modeled burst temporal width (bottom panel). The error weighted mean burst DM is 567.8$\pm$0.1 pc cm$^{-3}$, significantly larger than the long-term average of 560.5 pc cm$^{-3}$ seen by Arecibo during this campaign. However, we note that the 95\% confidence intervals in DM for multiple bursts are not consistent with this mean nor each other, which suggests that some burst-specific property can bias the measured DM. The variation in DM observed by the VLA at 3~GHz is similar to that reported for Arecibo observations of \frb\ in \citet{2016arXiv160308880S}.
% This is consistent with the idea that the DM measured at low temporal resolution (e.g., by the VLA or by single-dish observatories without coherent dedispersion) is determined by extrinsic (an electron column) dispersion and some spectrotemporal structure that changes between bursts.
